Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-05 WSSSPE1_report/WSSSPE1_summary_report.tex
small changes in process section

\begin{itemize}[leftmargin=0.2in]
\item the development process that leads to new (versions of) software
\begin{itemize}[leftmargin=0.2in]
\item how fundamental research in computer science or
  science/engineering domains is turned into reusable software
\item software created as a by-product of research
\item impact of computer science research on the development of
  scientific software
\end{itemize}
\item the support and maintenance of existing software, including
  software engineering
\begin{itemize}[leftmargin=0.2in]
\item governance, business, and sustainability models
\item the role of community software repositories, their operation and
  sustainability
\end{itemize}
\item the role of open source communities or industry
\item use of the software
\begin{itemize}[leftmargin=0.2in]
\item growing communities
\item reproducibility, transparency needs that may be unique to science
\end{itemize}
\item policy issues, such as
\begin{itemize}[leftmargin=0.2in]
\item measuring usage and impact
\item software credit, attribution, incentive, and reward
\item career paths for developers and institutional roles
\item issues related to multiple organizations and countries,
  such as intellectual property, licensing, etc.
\item mechanisms and venues for publishing software, and the role of
  publishers
\end{itemize}
\item education and training
\end{itemize}

@@

58 submissions were received, and almost all submitters used either
arXiv~\cite{arXiv-web} or figshare~\cite{figshare-web} to self-publish
their papers.  A peer review process followed the submissions, where
the 58 papers received 181 reviews, an average of 3.12 reviews per
paper. Reviews were completed using a Google form, which allowed
reviewers to choose papers they wanted to review, then to provide
scores on their relevance and general comments to the organizers and
to the authors. The review reports enabled the organizers to decide
which papers to associate with the workshop, and allowed the authors
to improve their papers.

>>>>

\begin{itemize}[leftmargin=0.2in]
\item the development process that leads to new (versions of) software
\begin{itemize}[leftmargin=0.2in]
\item how fundamental research in computer science or
  science/engineering domains is turned into reusable software
\item software created as a by-product of research
\item impact of computer science research on the development of
  scientific software
\end{itemize}
\item the support and maintenance of existing software, including
  software engineering
\begin{itemize}[leftmargin=0.2in]
\item governance, business, and sustainability models
\item the role of community software repositories, their operation and
  sustainability
\end{itemize}
\item the role of open source communities or industry
\item use of the software
\begin{itemize}[leftmargin=0.2in]
\item growing communities
\item reproducibility, transparency needs that may be unique to science
\end{itemize}
\item policy issues, such as
\begin{itemize}[leftmargin=0.2in]
\item measuring usage and impact
\item software credit, attribution, incentive, and reward
\item career paths for developers and institutional roles
\item issues related to multiple organizations and multiple countries,
  such as intellectual property, licensing, etc.
\item mechanisms and venues for publishing software, and the role of
  publishers
\end{itemize}
\item education and training
\end{itemize}

@@

58 submissions were received, and almost all submitters used either
arXiv~\cite{arXiv-web} or figshare~\cite{figshare-web} to self-publish
their papers.

A peer review process followed the submissions, where
the 58 papers received 181 reviews, an average of 3.12 reviews per
paper. Reviews were completed using a Google form, which allowed
reviewers to choose papers they wanted to review, then to provide
general comments and scores on relevance to the organizers and
to the authors. The review reports enabled the organizers to decide
which papers to associate with the workshop, and allowed the authors
to improve their papers.
